%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Organization
    {Active-Active Cluster Server} % Project 
    {} % Date(s)
    {} % Location
    {
      \vspace{-1.2em}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineered critical components supporting complex system operations, including boot/shutdown sequencing, RMA management procedures, configuration synchronization, and plugin integrations.}
        \item {Managed concurrency issues and improved system stability and performance in high-load, dual-active environments.}
        \item {Spearheaded proactive monitoring solutions to quickly identify, diagnose, and resolve potential bottlenecks and system vulnerabilities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {}
    {High Availability System (Active-Passive)} % Job title
    {} % Date(s)
    {} % Location
    {
      \vspace{-1.2em}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed robust modules for efficient system-level synchronization, reliable binding, and automated failover mechanisms.}
        \item {Leveraged critical technologies including DRBD, Pacemaker, Corosync, rsync, lsyncd, and systemd to ensure seamless high-availability solutions.}
        \item {Optimized system performance and minimized downtime through targeted enhancements and rigorous system testing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Organization
    {Bare-Metal Backup \& Restore for DSM} % Job title
    {} % Date(s)
    {} % Location
    {
      \vspace{-1.2em}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Directed the integration and optimization of comprehensive block-level backup and restore operations, ensuring end-to-end data integrity.}
        \item {Designed and implemented advanced communication and coordination mechanisms leveraging IPC for efficient inter-module operations.}
        \item {Collaborated extensively with multiple teams to streamline disaster recovery processes and enhance user experience through improved reliability and faster recovery times.}
      \end{cvitems}
    }
  
\end{cventries}